### 2014-04-08 presentation/graphic/time_line.tex
fixed graphic
more presentation stuff

	\begin{tikzpicture} [scale=.5]
		\draw [thick] (6,6) -- (10,6) -- (10,3.5) -- (6,3.5) -- (6,6);
		\draw [thick] (14.5,6) -- (10.5,6) -- (10.5,3.5) -- (14.5,3.5) -- (14.5,6);
		\node[align=center] at (2.5,4.75) {\textbf{Tiles to assign:}};
		\node[align=center, above] at (8,6) {Group 1};
		\node[align=center, above] at (12.5,6) {Group 2};
		\node[align=center, box, draw] at (7,4.75) {13\\9};
		\node[align=center, box, draw] at (9,4.75) {11\\13};
		\node[align=center, box, draw] at (12.5,4.75) {9\\12};		
		\draw [thick] (-4,2) -- (18,2);

@@

		\node[align=center, box, draw] at (7,.5) {13\\9};
		\node[align=center] at (8.5,.5) {1.5};
		\node[align=center, box, draw, fill = green] at (14,.5) {11\\13};
		\node[align=center] at (15.5,.5) {0.5};

@@

		\node[align=center, box, draw, fill = green] at (14,-2) {13\\9};
		\node[align=center] at (15.5,-2) {1.0};

@@

		\node[align=center, box, draw, fill = orange] at (7,-2) {11\\13};
		\node[align=center] at (8.5,-2) {5.0};

@@

		\node[align=center, box, draw, fill = green] at (14,-4.5) {9\\12};
		\node[align=center] at (15.5,-4.5) {1.6};

@@

		\node[align=right] at (-1,3.2) {\scriptsize \textbf{Reference}};
		\node[align=right] at (-1,2.5) {\scriptsize \textbf{Protein Chain}};
		\node[align=right] at (-2.5,1.5) {\tiny Chemical Shift};
		\node[align=right] at (.25,1.5) {\tiny Group};
		\node[align=right] at (-2.5,.5) {11.5};
		\node[align=right] at (-2.5,-2) {12.5};
		\node[align=right] at (-2.5,-4.5) {9.6};
		\node[align=right] at (.25,.5) {1};
		\node[align=right] at (.25,-2) {1};
		\node[align=right] at (.25,-4.5) {2};

>>>>

	\begin{tikzpicture} [scale=.5]
		\draw [thick] (6,6) -- (10,6) -- (10,3.5) -- (6,3.5) -- (6,6);
		\draw [thick] (14.5,6) -- (10.5,6) -- (10.5,3.5) -- (14.5,3.5) -- (14.5,6);
		\node[align=center] at (0,4.75) {\textbf{Tiles to assign:}};
		\node[align=center] at (4.25,4.75) {$i-1$\\$i$};
		\draw [thick] (5.5,6) -- (3,6) -- (3,3.5) -- (5.5,3.5) -- (5.5,6);
		\node[align=center, above] at (8,6) {Group 1};
		\node[align=center, above] at (12.5,6) {Group 2};
		\node[align=center, rounded corners, box, draw] at (7,4.75) {9\\12};
		\node[align=center, rounded corners, box, draw] at (9,4.75) {11\\13};
		\node[align=center, rounded corners, box, draw] at (12.5,4.75) {13\\9};		
		\draw [thick] (-4,2) -- (18,2);

@@

		\node[align=center, rounded corners, box, draw] at (7,.5) {9\\12};
		\node[align=center] at (8.5,.5) {1.5};
		\node[align=center, rounded corners, box, draw, fill = green] at (14,.5) {11\\13};
		\node[align=center] at (15.5,.5) {0.5};

@@

		\node[align=center, rounded corners, box, draw, fill = green] at (14,-2) {13\\9};
		\node[align=center] at (15.5,-2) {1.0};

@@

		\node[align=center, rounded corners, box, draw, fill = orange] at (7,-2) {13\\9};
		\node[align=center] at (8.5,-2) {3.0};

@@

		\node[align=center, rounded corners, box, draw, fill = green] at (14,-4.5) {9\\12};
		\node[align=center] at (15.5,-4.5) {1.6};

@@

		\node[align=right] at (-1,3.2) {\scriptsize \textbf{Reference}};
		\node[align=right] at (-1,2.5) {\scriptsize \textbf{Protein Chain}};
		\node[align=right] at (-2.5,1.5) {\tiny Chemical Shift};
		\node[align=right] at (.25,1.5) {\tiny Group};
		\node[align=right] at (-2.5,.5) {13.5};
		\node[align=right] at (-2.5,-2) {9.5};
		\node[align=right] at (-2.5,-4.5) {11.4};
		\node[align=right] at (.25,.5) {1};
		\node[align=right] at (.25,-2) {2};
		\node[align=right] at (.25,-4.5) {1};
